1.comments in javascript
    html       :- <!--  content  -->
    css        :- /* css /
    javascript :- // for single line
                    /* mutliline */

2. what is a variable :-
                The Variable is a container to storing the data or store the data value.
                
                for eg. var x=2;    var name="username";    var bool="true";
                    i.e. the var is variable, x is a user defined name, 2 is the value assigned by user, ; semicolon used for end of line.
                In javascript there are 3 way to declare variable 1-var, 2-let, 3-const.

            limitations:- 
                -varible name must be non-reserved keyward.
                -Could't not use first letter as number.
            
3. how many way to run javascript file?
    there are two way in website assigned   
        1- using node js (instlling required).
        eg. node filename.js
        2- using html file but js file must be linked with htmlfile and see the output in console tab on inspect on brower page.

4. what is data type in javascript.?
    The javascript variable hold the information is also called as the data type data,
    data type  as 100 number and string as name,  string written in quotes("") and number written without quotes. 
    
5. Type of Data type in javascript?
    Two number of data in javascript as a
        - Primitive data type.(Number, String, Boolean, Null, Undefined, Symbol)
        - Non-Primitive data type.(object, array)

6. difference between NULL and Undefined ?
    Null is data type that has define as Null value.
    eg var age=Null;  typeof->object
    undefined is data type that not defined value or not assign value by user simple its create first.  
    eg. var name;  typeof->undefined       

7.  